%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Master's Degree in Artificial Intelligence and Cybersecurity{\enskip\cdotp\enskip}110 cum Laude}
    {University of Enna "Kore"}
    {Enna, Italy}
    {2022 - 2024}
    {
      \begin{cvitems}
        \item {Specialization in \textbf{Machine Learning and Artificial Intelligence}: design and implementation of \textbf{classification, regression and clustering} models using \textbf{Python}.}
        \item {Experience with major ML algorithms: \textbf{logistic regression, support vector machines, neural networks, gaussian mixture models, k-means clustering}.}
        \item {Application of \textbf{dimensionality reduction} techniques (\textbf{PCA, LDA}) and model evaluation through statistical metrics and decision theory.}
        \item {Design of \textbf{intelligent systems}: intelligent agents, search algorithms, knowledge representation, \textbf{Bayesian networks} and multi-agent systems.}
        \item {Skills in \textbf{Human-Centered AI}: design of user-centered AI systems, evaluation of \textbf{user experience}, usability, security, and ethical aspects of artificial intelligence.}
        \item {Experience in \textbf{Speech Processing and Computational Linguistics}: speech recognition, speech synthesis, speaker recognition, signal processing and statistical language models.}
        \item {Advanced skills in \textbf{Cybersecurity}: authentication, access control, network and operating system security, database security and security protocols.}
        \item {Analysis of \textbf{cyber attacks and network vulnerabilities}, incident management, \textbf{ethical hacking} techniques and IT infrastructure protection.}
        \item {Study of \textbf{AI for Security}: adversarial attacks in machine learning models and use of AI for cyber threat detection.}
        \item {Design of \textbf{biometric systems}: facial recognition, fingerprints, iris recognition and multi-biometric authentication systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bachelor's Degree in Computer Engineering{\enskip\cdotp\enskip}96 / 110}
    {University of Enna "Kore"}
    {Enna, Italy}
    {2019 - 2022}
    {
      \begin{cvitems}
        \item {Solid foundation in \textbf{Computer Science fundamentals}: algorithms, data structures, computer architecture and algorithm design for engineering problem solving.}
        \item {Software development in \textbf{C, Java and Python} with \textbf{object-oriented} design, \textbf{UML} modeling and implementation of modular, reusable applications.}
        \item {Design and management of \textbf{relational databases}: conceptual and logical modeling, normalization and querying with \textbf{SQL/MySQL (DDL, DML)}.}
        \item {Skills in \textbf{Operating Systems and Concurrency}: process and thread management, synchronization (mutex, semaphores), IPC and system programming in \textbf{C on Unix/Linux}.}
        \item {Fundamentals of \textbf{Computer Networks}: Internet protocols, network and transport layers, IP addressing and network performance analysis.}
        \item {Introduction to \textbf{Machine Learning and Artificial Intelligence} with model development and software applications in the \textbf{Python} ecosystem.}
        \item {Principles of \textbf{Cybersecurity and cryptography}: encryption algorithms, authentication and design of secure software solutions.}
        \\
      \end{cvitems}
    }
  \cventry
    {Classical High School Diploma}
    {Liceo Classico Tommaso Fazello}
    {Sciacca, Italy}
    {}
    {
      \begin{cvitems}
        \item {Humanistic education developing \textbf{critical analysis, communication skills and problem solving}.}
        \\
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
